Tom Stafford, Professor of Cognitive Science

### 2024-02-04 index.qmd
come on now
new
new2
wip

---
title: "Tom Stafford, Professor of Cognitive Science"
format: html
editor: visual
---

@@

@@

<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" width="500" height="800" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=false&boosts=false"></iframe>

Colophon

Website made with [Quarto](https://quarto.org), hosted on github pages. Styles taken from <https://ddimmery.com/posts/quarto-website/>

>>>>

---
title: "Tom Stafford, Professor of Cognitive Science"
format: html
page-layout: full
image: /tom_2020.jpg
---

::: {.html}
<style>
  iframe {
    width: 100%;
    aspect-ratio: 500 / 800;
    max-width: 500px; /* Optional */
  }
</style>
:::

@@

HI

@@

<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=true&boosts=false"></iframe>
Colophon

Website made with [Quarto](https://quarto.org), hosted on [github](https://github.com/tomstafford/tomstafford.github.io). Styles taken from <https://ddimmery.com/posts/quarto-website/>
